Deep Reinforcement Learning for Conservation Decisions

### 2021-08-12 manuscript/manuscript.Rmd
Added a sentence on sample efficiency

An environment is a mathematical function, computer program, or real world experience that takes an agent's proposed *action* as input and returns an observation of the environment's current *state* and an associated *reward* as output.
In contrast to classical approaches [@Marescot2013], there are few restrictions on what comprises a state or action. 
States and actions may be continuous or discrete, completely or partially observed, single or multidimensional.
The main focus of building an RL environment, however, is on the environment's transition dynamics and reward function.
The designer of the environment can make the environment follow any transition and reward function provided that both are functions of the current state and action.
This ability allows RL environments to model a broad range of decision making problems.
For example, we can set the transitions to be deterministic or stochastic.
We can also specify the reward function to be *sparse*, whereby a positive reward can only be received after a long sequence of actions, e.g. the end point in a maze.
In other environments, an agent may have to learn to forgo immediate rewards (or even accept an initial negative reward) in order to maximize the net discounted reward as we illustrate in examples here.

@@

<!-- Model free is great bc we don't know the true models -->
The rapidly expanding class of model-free RL algorithms is particularly appealing given the ubiquitous presence of model uncertainty in ecological dynamics.
Rarely do we know the underlying functional forms for ecological processes.
Methods which must first assume something about the structure or functional form of a process before estimating the corresponding parameter can only ever be as good as those structural assumptions.
Frequently available ecological data is insufficient to distinguish between possible alternative models [@knape_are_2012], or the correct model may be non-identifiable with any amount of data.
Model-free RL approaches offer a powerful solution for this thorny issue.
Model-free algorithms have proven successful at learning effective policies even when the underlying model is difficult or impossible to learn [@Pong2020], as long as simulations of possible mechanisms are available.

>>>>

An environment is a mathematical function, computer program, or real world experience that takes an agent's proposed *action* as input and returns an observation of the environment's current *state* and an associated *reward* as output.
In contrast to classical approaches [@Marescot2013; @chades_primer_2021], there are few restrictions on what comprises a state or action. 
States and actions may be continuous or discrete, completely or partially observed, single or multidimensional.
The main focus of building an RL environment, however, is on the environment's transition dynamics and reward function.
The designer of the environment can make the environment follow any transition and reward function provided that both are functions of the current state and action.
This ability allows RL environments to model a broad range of decision making problems.
For example, we can set the transitions to be deterministic or stochastic.
We can also specify the reward function to be *sparse*, whereby a positive reward can only be received after a long sequence of actions, e.g. the end point in a maze.
In other environments, an agent may have to learn to forgo immediate rewards (or even accept an initial negative reward) in order to maximize the net discounted reward as we illustrate in examples here.

@@

<!-- Model free is great bc we don't know the true models -->
The rapidly expanding class of model-free RL algorithms is particularly appealing given the ubiquitous presence of model uncertainty in ecological dynamics.
Rarely do we know the underlying functional forms for ecological processes.
Methods which must first assume something about the structure or functional form of a process before estimating the corresponding parameter can only ever be as good as those structural assumptions.
Frequently available ecological data is insufficient to distinguish between possible alternative models [@knape_are_2012], or the correct model may be non-identifiable with any amount of data.
Model-free RL approaches offer a powerful solution for this thorny issue.
Model-free algorithms have proven successful at learning effective policies even when the underlying model is difficult or impossible to learn [@Pong2020], as long as simulations of possible mechanisms are available.
Yet, model-free algorithms tend to have poor sample efficiency [@sac] which may restrain them from being insightful on simulators that are slow to run.
